--- 
title: "Report Title"
subtitle: "Prepared for: Client Name"
author: 
- Primary Statistician, Statistician
- Secondary Statistician, Statistician
- Director Name, Director
authors: 
  name: Primary Statistician  
  affiliation: Statistical Consulting and Research Services  

secondary: 
  name: Secondary Statistician
  affiliation: Statistical Consulting and Research Services
director:  
  name: Director Name
  affiliation: Statistical Consulting and Research Services  

abstract: |
  **Author Note:**  
  
  This material is provided to communicate advice from SCRS statisticians based on our best understanding of your research needs. We encourage you to use this report in discussions with colleagues. Please do not publish any portion of this material without permission.  
  
  © Primary Statistician
  
  When you make use of our work for publications or presentations, please be sure to acknowledge the funding we receive from NIGMS using the following: “Research reported in this publication was supported by Institutional Development Awards (IDeA) from the National Institute of General Medical Sciences of the National Institutes of Health under Awards P20GM103474, U54GM115371, 5P20GM104417, and 2U54GM104944-06. The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.  
prelim: yes
date: "**`r format(Sys.time(), '%B %d, %Y')`**"
titlepage: yes
msucolor: yes
twoside: yes
spacing: 1
bibliography: [scrs-ref.bib, packages.bib]
biblio-style: apalike
link-citations: yes
colorlinks: yes
site: bookdown::bookdown_site
documentclass: article
---


```{r import, echo = FALSE}
# Some other useful knitr options:
# fig.retina: multiplicative factor for figures' resolution
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, message = FALSE,
               comment = NA, size = 'footnotesize', width = 80,
               warning = FALSE, show.signif.stars = FALSE,
               fig.height=5, fig.width=10)
```

```{r packages, include=FALSE}
# automatically create a bib database for R packages, list used packages here
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'readr', 'readxl', 'dplyr', 'mosaic',
  'nlme', 'yarrr', 'predictmeans','tibble', 'ggplot2', 'effects'), 'packages.bib')
```

```{r echo=F}
# load all required packages first, edit this list as required.
library(readr)
library(readxl)
library(dplyr)
library(mosaic)
library(knitr)
library(yarrr)
library(nlme)
library(predictmeans)
library(effects)
library(tibble)
suppressMessages(library(stringr))
```

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(prerequisites).


# Body of the report

When writing your report it is important to use proper header levels. Each main section should start with one octothorpe ("#"). Sub-sections should start with two octothorpes ("##"), and so on. Make sure there is a space after each octothorpe and before the section title.

## Including Figures and Tables created by R code

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

### Adding a Figure

Make sure that figures have a `fig.cap` (figure caption). You can use either `out.width` for sizing or `fig.height` and `fig.width`. To get R to scale graphics appropriately I find that oversizing a figure works nicely. For example, even though letter paper is 8.5" x 11" I will set a figure that I want to use half the page to `fig.width=10` and `fig.height=6`.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). 

### Adding a Table

Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

## Including graphics or figures not created by R

Did you know the `yarr` package has several images in it? The images are there because they were used to create the palates in the package. Let's import one of those images. Since I don't know where the `yarrr` package is stored on your computer and the delimiter used by your operating system, I will use R functions to find the path and to create the file path.

```{r fig.cap="Finding nemo image from yarr package.", out.width="80%"}
knitr::include_graphics(file.path(path.package("yarrr"), "nemo.jpg"))
```

## Including citations

You can write citations, too. For example, this is R [@R] and the most referenced book is [@Ramsey2012].

If a package is used and cited it will be included in the references section. Edit the following list of packages below.

# Packages used

The R package `bookdown` [@R-bookdown] was used to create this report document using the `R` language [@R-base]. In addition, the following were packages used for the analysis and/or formatting of this document:

- `knitr` [@R-knitr]
- `rmarkdown` [@R-rmarkdown]
- `readr` [@R-readr]
- `readxl` [@R-readxl]
- `tibble` [@R-tibble]
- `dplyr` [@R-dplyr]
- `mosaic` [@R-mosaic]
- `nlme` [@R-nlme]
- `yarrr` [@R-yarrr]
- `ggplot2` [@R-ggplot2]
- `effects` [@R-effects]
- `predictmeans` [@R-predictmeans]

# References

