--- 
title: "Most Important Study"

author: "R.A. Fisher"
client: "Client Name"
director: "Mark Greenwood, Ph.D."
secondary: "Secondary Statistician"
prelim: yes
date: "`r format(Sys.time(), '%B %d, %Y')`"
titlepage: yes
msucolor: yes
twoside: yes
spacing: 1
bibliography: scrs-ref.bib
biblio-style: apalike
link-citations: yes
colorlinks: yes
site: bookdown::bookdown_site
documentclass: article
---

```{r import, echo = FALSE}
# Some other useful knitr options:
# collapse: show a button to show/hide the source code
# fig.retina: multiplicative factor for figures' resolution
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE,
               comment = NA, size = 'footnotesize', width = 80,
               warning = FALSE, show.signif.stars = FALSE)

# Limit the displayed decimals at 2
options(digits = 2)
```

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(prerequisites).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, this is R [@R] and one the most referenced book is [@Ramsey2012].
